Blocking-resistant communication\\through domain fronting

### 2014-07-22 docs/meek.tex
Straight apostrophes in shell command.
Cite obfs4.

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}

@@

\noindent
\begin{quote}
\usefont{U}{cmtt}{m}{n}%
\$ wget -q -O - https://www.google.com/ \char`\\\\
\strut~~~~--header 'Host: maps.google.com' | \char`\\\\
\strut~~~~grep -o '<title>.*</title>'\\
<title>Google Maps</title>
\end{quote}

@@

To the above challenges we may add the related challenge of active probing.
An active-probing censor tries to connect to a server using a circumvention tool
as if it were an ordinary client.
If the connection is successful, the server can be blacklisted.
Active probing is a very precise means of identifying a server as belonging to a circumvention system.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing followup scans to observed client connections to see
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit}
and in this work.

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{graphicx}
\usepackage{url}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{textcomp}

@@

\noindent
\begin{quote}
\usefont{U}{cmtt}{m}{n}%
\$ wget -q -O - https://www.google.com/ \char`\\\\
\strut~~~~--header \textquotesingle{}Host: maps.google.com\textquotesingle{} | \char`\\\\
\strut~~~~grep -o \textquotesingle{}<title>.*</title>\textquotesingle{}\\
<title>Google Maps</title>
\end{quote}

@@

To the above challenges we may add the related challenge of active probing.
An active-probing censor tries to connect to a server using a circumvention tool
as if it were an ordinary client.
If the connection is successful, the server can be blacklisted.
Active probing is a very precise means of identifying a server as belonging to a circumvention system.
Winter and Lindskog~\cite{foci12-winter} confirmed an earlier discovery of
Wilde~\cite{wilde} that China's Great Firewall identifies Tor bridges
by issuing followup scans to observed client connections to see
whether a server speaks the Tor protocol.
The discovery of active probing was the motivation for probing resistance in ScrambleSuit~\cite{scramblesuit},
obfs4~\cite{obfs4},
and this work.
